Finding ARG1 of Partitive Nouns in NomBank with DistilBERT

### 2022-05-03 src/paper.tex
Update

NomBank (Meyers et al., 2004c) is a databank project at New York University that adds annotation layer of argument structure for instances in the Penn Treebank II corpus. Apart from the more commonly researched nominalizations of verbs and nominalizations of adjectives, it also covers relational nouns, partitive nouns and several other types of types of argument-taking nouns.

@@

\section{Engines}

To produce a PDF file, pdf\LaTeX{} is strongly recommended (over original \LaTeX{} plus dvips+ps2pdf or dvipdf). Xe\LaTeX{} also produces PDF files, and is especially suitable for text in non-Latin scripts.

>>>>

NomBank (Meyers et al., 2004c) is a databank project at New York University that adds annotation layer of argument structure for instances in the Penn Treebank II corpus. Apart from the more commonly researched nominalizations of verbs and nominalizations of adjectives, it also covers relational nouns, partitive nouns and several other types of argument-taking nouns.

@@

\section{Related Work}

NomBank (Meyers et al., 2004c), as a databank extending the frames of NOMLEX and PropBank, annotates argument structures of common nouns similar to how PropBank annotates predicating verbs. The development of the NomBank corpus has supported the work of (Jiang and Ng, 2006) and (Liu and Ng, 2007). Each study tested the hypothesis that machine learning methodologies and representations used in verbal SRL (cf. (Pradhan et al., 2005)) can be ported to the task of NomBank SRL. (Liu and Ng, 2007) reports an overall f-measure score of 0.7283 using automatically generated parse trees, demonstrating that modest performance can be achieved using basic approaches developed in the verbal domain. Both studies also investigated the use of features specific to the task of nominal SRL, but observed only marginal performance gains.
